Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-12-04 ATACCC-appendix-original-analysis.tex
Updates from Overleaf

\begin{figure}
    \centering
    \makebox[\textwidth][c]{\includegraphics[scale=0.8]{ATACCC/appendix/Bayesian_piecewise_DAG}}
    \caption{Directed acyclic graph showing the relationship between parameters in the model. Dotted lines represent deterministic (functional) relationships and solid lines stochastic (distributional) relationships. The box represents a fixed (known) quantity and double circle an observed quantity (the data). Index $i$ ranges over individuals, and $t$ over time. Parameters indexed by $i$ exist once for each individual. See main text for equations governing the relationships and the distributions used.}
    \label{fig:paper:model_DAG}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
    Parameter & Distribution & 0.05 & 0.5 & 0.95 \\ 
  \hline
    $\eta$ & $\text{Beta}(0.95, 9)$ & $0$ & $0.07$ & $0.28$ \\ 
    $\sigma_\text{obs}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\ 
    $t_{0,i}$ & $N(0, 5^2)$ & $-8.22$ & $0$ & $8.22$ \\ 
    $\mu_{\log t_\text{peak}}$ & $N(\log(3), \log(2.5)^2)$ & $\log (0.66)$ & $\log (3)$ & $\log (13.54)$ \\ 
    $\sigma_{\log t_\text{peak}}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\ 
    $\mu_{C_\text{peak}}$ & $N(17, 5^2)$ & $8.78$ & $17$ & $25.22$ \\ 
    $\sigma_{C_\text{peak}}$ & $\text{Half-Cauchy}(0, 4)$ & $0.31$ & $4$ & $50.82$ \\ 
    $\mu_{\log\beta}$ & $N(\log(3.5), \log(1.4)^2)$ & $\log (2.01)$ & $\log (3.5)$ & $\log (6.09)$ \\ 
    $\sigma_{\log\beta}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\
   \hline
\end{tabular}
\caption{Priors used, columns 3 to 5 gives quantiles of the distributions specified. See main text for description of the parameters.}
\label{tab:paper:priors}
\end{table}

@@

\begin{figure}
    \centering
    \vspace*{-3cm}
    \makebox[\textwidth][c]{\includegraphics[scale=0.9]{ATACCC/appendix/goodness_of_fit}}
    \caption{Predictive median (solid line), 50\% and 95\% predictive intervals (light and dark shading respectively) for test results (ignoring false negatives). Points show actual observations.}
    \label{fig:paper:goodness_of_fit}
\end{figure}

@@

The time between the two points when $\hat{C} = C_\text{lod}$ for an individual can be considered a duration of infection.
This gives a mean duration estimated at 18.4 (16.5--20.9) days but the distribution is skewed, as seen by the median of 16.6 (14.8--18.5) days.
The full distribution is in \cref{fig:paper:duration}.
\begin{figure}
    \centering
    \makebox[\textwidth][c]{\includegraphics{ATACCC/appendix/duration}}
    \caption{Proportion of people with $\hat{C} > C_\text{lod}$ a given number of days after this first occurred. Shading indicates central 95\% credible interval.}
    \label{fig:paper:duration}
\end{figure}

@@

\begin{table}[]
    \centering
    \makebox[\textwidth][c]{\begin{tabular}{p{7cm}ccc}
    Quantity & This study & \Textcite{kisslerViral} \\ 
    \hline
    Mean time from first detectable to peak viral load / days & 2.4 (1.5--3.3) & 3.2 (2.4--4.2) \\
    Mean Ct at peak viral load / Ct & 17.8 (17.1--18.6) & 22.4 (20.7--24.0) \\
    Mean increase in Ct following peak / Ct / day & 1.6 (1.5--1.8) & 2.1 (1.7--2.6)
    \end{tabular}}
    \caption{Summary of results in comparison to previous studies. \Textcite{jonesEstimating} do not give values in terms of Ct.}
    \label{tab:paper:compare}
\end{table}

>>>>

\begin{figure}
    \centering
    \makebox[\textwidth][c]{\includegraphics[scale=0.8]{ATACCC/appendix/Bayesian_piecewise_DAG}}
    \caption[DAG showing hiearchical structure]{Directed acyclic graph showing the relationship between parameters in the model. Dotted lines represent deterministic (functional) relationships and solid lines stochastic (distributional) relationships. The box represents a fixed (known) quantity and double circle an observed quantity (the data). Index $i$ ranges over individuals, and $t$ over time. Parameters indexed by $i$ exist once for each individual. See main text for equations governing the relationships and the distributions used.}
    \label{fig:paper:model_DAG}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
    Parameter & Distribution & 0.05 & 0.5 & 0.95 \\ 
  \hline
    $\eta$ & $\text{Beta}(0.95, 9)$ & $0$ & $0.07$ & $0.28$ \\ 
    $\sigma_\text{obs}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\ 
    $t_{0,i}$ & $N(0, 5^2)$ & $-8.22$ & $0$ & $8.22$ \\ 
    $\mu_{\log t_\text{peak}}$ & $N(\log(3), \log(2.5)^2)$ & $\log (0.66)$ & $\log (3)$ & $\log (13.54)$ \\ 
    $\sigma_{\log t_\text{peak}}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\ 
    $\mu_{C_\text{peak}}$ & $N(17, 5^2)$ & $8.78$ & $17$ & $25.22$ \\ 
    $\sigma_{C_\text{peak}}$ & $\text{Half-Cauchy}(0, 4)$ & $0.31$ & $4$ & $50.82$ \\ 
    $\mu_{\log\beta}$ & $N(\log(3.5), \log(1.4)^2)$ & $\log (2.01)$ & $\log (3.5)$ & $\log (6.09)$ \\ 
    $\sigma_{\log\beta}$ & $\text{Half-Cauchy}(0, 0.67)$ & $0.05$ & $0.67$ & $8.51$ \\
   \hline
\end{tabular}
\caption[Priors]{Priors used, columns 3 to 5 gives quantiles of the distributions specified. See main text for description of the parameters.}
\label{tab:paper:priors}
\end{table}

@@

\begin{figure}
    \centering
    \vspace*{-3cm}
    \makebox[\textwidth][c]{\includegraphics[scale=0.9]{ATACCC/appendix/goodness_of_fit}}
    \caption[Goodness-of-fit]{Predictive median (solid line), 50\% and 95\% predictive intervals (light and dark shading respectively) for test results (ignoring false negatives). Points show actual observations.}
    \label{fig:paper:goodness_of_fit}
\end{figure}

@@

The time between the two points when $\hat{C} = C_\text{lod}$ for an individual can be considered a duration of infection.
This gives a mean duration estimated at 18.4 (16.5--20.9) days but the distribution is skewed, as seen by the median of 16.6 (14.8--18.5) days.
The full distribution is in \cref{fig:paper:duration}.
\begin{figure}
    \centering
    \makebox[\textwidth][c]{\includegraphics{ATACCC/appendix/duration}}
    \caption[Proportion of population positive]{Proportion of people with $\hat{C} > C_\text{lod}$ a given number of days after this first occurred. Shading indicates central 95\% credible interval.}
    \label{fig:paper:duration}
\end{figure}

@@

\begin{table}[]
    \centering
    \makebox[\textwidth][c]{\begin{tabular}{p{7cm}ccc}
    Quantity & This study & \Textcite{kisslerViral} \\ 
    \hline
    Mean time from first detectable to peak viral load / days & 2.4 (1.5--3.3) & 3.2 (2.4--4.2) \\
    Mean Ct at peak viral load / Ct & 17.8 (17.1--18.6) & 22.4 (20.7--24.0) \\
    Mean increase in Ct following peak / Ct / day & 1.6 (1.5--1.8) & 2.1 (1.7--2.6)
    \end{tabular}}
    \caption[Comparison to previous studies.]{Summary of results in comparison to previous studies. \Textcite{jonesEstimating} do not give values in terms of Ct.}
    \label{tab:paper:compare}
\end{table}

### 2023-12-04 thesis.tex
Updates from Overleaf

\chapter{Conclusion}
Household structure is not included in this model.
The household-based design of the survey is likely to induce clustering in results, increasing the variance of the measured prevalence.
The beta-binomial likelihood structure should capture some of this variance within each strata\todo{ref beta-binomial as a model for clustering}, but not between strata.

>>>>

\chapter{Conclusion}
